---
title: "Lab 02 - Plastic waste"
author: "Natalie Frye"
date: "2/7/21"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

The continents seems to be fairly similar in their plastic waste per capita. North America has one or two outliers of countries with much higher high plastic waste per capita. 

```{r plastic-waste-continent}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2) +
  facet_wrap(~ continent)
```

### Exercise 2

```{r plastic-waste-density}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = .2)
```


### Exercise 3

Color and fill are defined using the aesthetics of the plot because we wanted them to be based on the value of variables in the dataset, whereas we wanted alpha to just be a property of the plot and not determined by the data, so we made it a characteristic of the plotting geom.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()
```

The violin plots allow you to see the density plot, which isn't in a regular box plot. The median and upper and lower quartiles of each distribution are more readily apparent in a regular box plot, since they are marked with distinct lines.

### Exercise 5

There seems to be a slightly positive linear relationship between mismanaged plastic waste per capita and plastic waste per capita.

```{r plastic-waste-mismanaged}
ggplot(data = plastic_waste, 
       mapping = aes(x = mismanaged_plastic_waste_per_cap, 
                     y = plastic_waste_per_cap)) +
  geom_point()
```

### Exercise 6

Europe and North America seems to have a stronger relationship between plastic waste and mismanaged plastic waste, while Africa seems to have a weaker relationship between the two.

```{r plastic-waste-mismanaged-continent}
ggplot(data = plastic_waste, 
       mapping = aes(x = mismanaged_plastic_waste_per_cap, 
                     y = plastic_waste_per_cap, color = continent)) +
  geom_point()
```

### Exercise 7

I wouldn't really say either variable looks more strongly linearly associated with plastic waste. Maybe the coastal population is slightly more so.

```{r plastic-waste-population-total}
ggplot(data = plastic_waste, 
       mapping = aes(x = total_pop, 
                     y = plastic_waste_per_cap, color = continent)) +
  geom_point()
```

```{r plastic-waste-population-coastal}
ggplot(data = plastic_waste, 
       mapping = aes(x = coastal_pop, 
                     y = plastic_waste_per_cap, color = continent)) +
  geom_point()
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
ggplot(data = plastic_waste, 
       mapping = aes(x = coastal_pop / total_pop, 
                     y = plastic_waste_per_cap, color = continent)) +
  geom_point(scatter.smooth())
```
